When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
corrected sca reporting

INSERT FIGURE 2 HERE
<!--
```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}

  include_graphics(here("06_Paper", "Stage 2", "Figures", "sca-plot.png"))

Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors and the largest effect of *n*-back level.
These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
The by far highest values of the beta of the median RT in Figure\ \@ref(fig:sca-plot) are all from the pipelines that used inverse transformation.

@@

INSERT FIGURE 3 HERE
<!--
```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level. Each dot indicates a participant, the colours indicate their Need for Cognition score. $N=116$. There is a horizontal jitter of 0.4 and a vertical jitter of 0.05for visual clarity.", fig.pos="H"}

  include_graphics(here("06_Paper", "Stage 2", "Figures", "nfc-sv.png"))

@@

  include_graphics(here("06_Paper", "Stage 2", "Figures", "h3a-plot.png"))

@@

The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across *n*-back levels.
The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit small.
In both cases, the SVs decreased when the value of the predictor increased.
The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not *d'* yielded significant differences across levels in the manipulation checks.
However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
Since more participants reported effort avoidance as their motivation in the effort discounting than those who reported seeking a challenge, we can assume that they were more motivated to repeat a task in which they performed well because their good performance coincided with low effort.

>>>>

INSERT FIGURE 2 HERE
```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))

Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors.
These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.

@@

INSERT FIGURE 3 HERE

```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level. Each dot indicates a participant, the colours indicate their Need for Cognition score. $N=116$. There is a horizontal jitter of 0.4 and a vertical jitter of 0.05for visual clarity.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfc-sv.png"))

@@

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))

@@

The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across *n*-back levels.
The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit less.
With increasing *n*-back level and decreasing *d'*, the SV decreased.
The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not *d'* yielded significant differences across levels in the manipulation checks.
However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
Since more participants reported effort avoidance as their motivation in the effort discounting than those who reported seeking a challenge, we can assume that they were more motivated to repeat a task in which they performed well because their good performance coincided with low effort.
